Embedded Meta-Learning: Toward more flexible deep-learning models

### 2019-08-01 writing/nips_submission/response/EML_response.tex
Newer scores

\textbf{miniImageNet \& datasets:} We didn't have time to evaluate on all the requested datasets, but on miniImageNet, using a ResNet as the input encoder, we achieved test accuracy of 62.4\% on 5-shot, 5-way classification, and 46.9\% on 1-shot, competitive with MAML and Meta-LSTM. We expect that with more than a few days to tune we could do better. Our tasks will be released on github as stand-alone python modules that other researchers can use. Developing more complex meta-learning datasets which include meta-mappings will be an important direction for future work.\par

>>>>

\textbf{miniImageNet \& datasets:} We didn't have time to evaluate on all the requested datasets, but on miniImageNet, using a ResNet as the input encoder, we achieved test accuracy of 63.2\% on 5-shot, 5-way classification, and 46.9\% on 1-shot, competitive with MAML and Meta-LSTM. We expect that with more than a few days to tune we could do better. Our tasks will be released on github as stand-alone python modules that other researchers can use. Developing more complex meta-learning datasets which include meta-mappings will be an important direction for future work.\par
